A weighted sampling algorithm to designing RNA sequences with target secondary structure and nucleotide distribution

### 2013-01-08 ISMB/methods_ISMB.tex

\subsection{Redesigning unpaired regions: A local/global hybrid approach}
Due to the simplification in our energy model, unpaired regions are not subject to design constraints other than the \GCContent, leading to modest similarities of refolded design candidates with the targeted structure. To improve these performances and test the complementarity  of our global sampling approach with previous contributions based on local search, we used the \RNAinverse software to redesign unpaired regions, specifying a constraint mask to prevent stacking base-pairs from being modified.
{\em todo: discuss evolution of \GCContent}

>>>>

\subsection{Redesigning unpaired regions: A local/global hybrid approach}
\label{subsec:glocal_method}
Due to the simplification in our energy model, unpaired regions are not subject to design constraints other than the \GCContent, leading to modest similarities of refolded design candidates with the targeted structure. To improve these performances and test the complementarity  of our global sampling approach with previous contributions based on local search, we used the \RNAinverse software to redesign unpaired regions, specifying a constraint mask to prevent stacking base-pairs from being modified.
{\em todo: discuss evolution of \GCContent}

### 2013-01-08 ISMB/supplementary_ISMB.tex

%!TEX root = main_ISMB.tex
\section{Supplementary data}
\subsection{Benchmark \ourprog vs \RNAinverse}
Using the same dataset of $50$ structures, we generated $100$ samples
per structure with \RNAinverse. They yield for most parameters
a high entropy. We present for every different concentration of \texttt{C+G}
the average sample entropy and the average base pairs entropy.

\begin{figure}[ht!]
	%\centering
	\hspace{-5em}
	\includegraphics[scale=0.4]{Figures/RNAinverse_data_100.png}
	\caption{Entropy and \texttt{C+G} content.}
	\label{fig:rnainverse}
\end{figure}

\subsection{Impact of local search on the \gc~content of \ourprog output}

>>>>

%!TEX root = main_ISMB.tex
\section{Supplementary data}
\subsection{Benchmark \ourprog vs \RNAinverse}
Using the same dataset of $50$ structures, we generated $100$ samples
per structure with \RNAinverse. They yield for most parameters
a high entropy. For all structures that have been solved 
by the three methods, only \RNAinverse, only \texttt{Incarnation} and
\texttt{Incarnation} followed by \RNAinverse,
we present for every different concentration of \texttt{C+G}
the average sample entropy and the average base pairs entropy.

\begin{figure}[ht!]
	%\centering
	\hspace{-5em}
	\includegraphics[scale=0.4]{Figures/RNAinverse_data_100.png}
	\caption{Entropy and \texttt{C+G} content for structures solved by
	the 3 methods.}
	\label{fig:rnainverse}
\end{figure}

%The same analysis but only for structures solved by \texttt{Incarnation}
%and \texttt{Incarnation} followed by \RNAinverse, is presented in 
%Fig.~\ref{fig:inc_rnainv}
%
%\begin{figure}
%	\centering
%	\includegraphics{}
%	\caption{Entropy and \texttt{C+G} content for structures solved by
%	the \texttt{Incarnation} and \texttt{Incarnation}$+$\RNAinverse.}
%	\label{fig:inc_rnainv}
%\end{figure}
\subsection{Impact of local search on the \gc~content of \ourprog output}
